---
title: "Rmarkdown/KnitR exercise"
author: "Smaragda Dimitrakopoulou"
date: "17 September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sampling 

We are going to sample 100 values from a log-normal distribution with mean equal to *1* and standard deviation equal to *0.25* and save them in the vector **_data_**

```{r Sampling}

data<-rlnorm(100, meanlog = 1, sdlog =0.25 )

```

## Histogram

The histogram of the 100 values is depicted below:

```{r Histogram, fig.cap="Histogram of the values"}

library(ggplot2)
data=data.frame(data)
ggplot(data=data,aes(x=data))  + geom_histogram(col="black",alpha=0.2,binwidth = 0.5)+labs(title="Histogram of the sampled values", x="Sampled Values", y="Frequency")


```

## Distribution on the log scale

The histogram of the transformed in the _log scale_ values can be depicted below.  
Note: the histogram is plotted also in the log scale.

```{r  Log Histogram, fig.cap="Log-Histogram of the values"}

ggplot(data=data,aes(x=log(data))) + scale_x_log10() + geom_histogram(col="black",alpha=0.2,binwidth = 0.05)+labs(title="Histogram of the log values", x="Log values in log scale", y="frequency")

```

## Mean and Variance of the Samples

The mean value of the samples is:


```{r  mean}
mean(data$data)
```

The variance of the samples is:


```{r  variance}
var(data$data)
```


